Sparse Function-space Representation \\ of Neural Networks

### 2023-05-22 paper/main.tex
UCI table

\begin{table}[t!] 
  \centering\scriptsize
  \caption{Negative log predictive density (NLPD) (lower better) for \our compared to GP subset based methods which discard most of the data.} 
	\label{tbl:uci-appendix}
	% Control table spacing
	\renewcommand{\arraystretch}{1.}
	\setlength{\tabcolsep}{2pt}
	\setlength{\tblw}{0.2\textwidth}

>>>>

\begin{table}[t!] 
  \centering\scriptsize
  \caption{Negative log predictive density (NLPD, lower better) for our \our method compared to a GP subset based method which discards most of the data. Even with a small $M$ our method is able to provide good results.} 
	\label{tbl:uci-appendix}
	% Control table spacing
	\renewcommand{\arraystretch}{1.}
	\setlength{\tabcolsep}{2pt}
	\setlength{\tblw}{0.25\textwidth}
